Thermodynamic fragments in magic state theories

### 2021-02-15 magic_paper.tex
Latex broken trying to do basic editing. Very annoying.

The more noisy the initial state is, the more copies needed to reach the target. 
We make this idea precise by defining the \emph{noise level threshold} as
\begin{equation}\label{eq:ethresh}
	\begin{split}
	\epsilon_{\rm{th}}(n, \tt, \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)\too{n}}{\sigma}}(x) \geq \\
	&{\lc{\rho(\epsilon')\too{\tt}}{\sigma}(x),\ x\in[0,1]\}}.
	\end{split}
\end{equation}
The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(n, \tt, \epsilon', \sigma)$.

\nick{Can also define a distillation bound
\begin{equation}\label{eq:ethresh}
	n_{\rm{th}}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{n: \lc{\noisysn}{\sigma} \geq \lc{\noisys(\epsilon')}{\sigma}\}}.
\end{equation}}

@@

In particular, the Wigner distribution of the state can be written as 
\begin{equation}
	\W[\bmx]{\noisys(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id},
\end{equation}
so we get positive components
\begin{equation}
	\wp(\epsilon) = \frac{1}{6} -\frac{1}{18}\epsilon
\end{equation}
at the 8 phase space points $\bmx \in \pd[3] \setminus \{\bmo\}$ and a negative component
\begin{equation}
	- \wn(\epsilon) = - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
\end{equation}
at the origin $\bmx = \bmo$.

@@

@@

We construct component and multiplicity vectors based on the distinct components of the Gibbs-rescaled distribution,
\begin{align}
	\bmm &\coloneqq (1,2,3,3) \\
	\bmw(\noisys) &\coloneqq (-\wn, \wp, \wp, \wp) \\
	\bmw(\gamma) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right) \\
	\bmw(\noisys | \gamma) &\coloneqq 3\Z \left( -\wn e^{\beta E_0}, \wp e^{\beta E_0}, \wp e^{\beta E_1}, \wp e^{\beta E_2} \right) \label{eq:bmw_rescaled}
\end{align}

There are four distinct values of the Gibbs-rescaled distribution on the phase space, with the negative Strange component $-\wn$ corresponding to energy $E_0$ as illustrated in the phase space split in~\cref{fig:pd_split_thermal}.
The Wigner-component vectors $\bmw(\noisys), \bmw(\gamma)$ are then constructed so as to match the four phase space regions.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
    \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
    The slope is negative in region $1$ and positive in regions $X,Y,Z$.
    It attains a unique value in each region, given by~\cref{eq:bmw_rescaled} respectively.
    }
    \label{fig:pd_split_thermal}
\end{figure}

For notational convenience, we define the index vector
\begin{equation}
	\bmq \coloneqq (n-\alpha,i,j,k),
\end{equation}
where $i,j,k$ are non-negative integers and
\begin{equation*}
	\alpha \coloneqq i+j+k \leq n.
\end{equation*}
The Wigner components of the $n$-copy distributions are now readily provided by~\cref{lem:ncopycomponents}.
Firstly, the $n$-copy multiplicity is given according to~\cref{eq:M} by
\begin{equation}
	m_{ijk} \coloneqq M_{\bmq} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
\end{equation}
The distribution values that correspond to the same index $\bmq$ are given according to~\cref{eq:W} by
\begin{align}
	w(\noisys)_{ijk} &= (-\wn)^{n-\alpha} \wp^{\alpha} \\
	w(\gamma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_0} e^{-\beta ( i E_0 + j E_1 + k E_2 )} \\
	w(\noisys | \gamma)_{ijk} &= (3\Z)^{n} (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )}
\end{align}

In order to construct the $n$-copy Lorenz curve of a Strange state in a thermal fragment we need to sort the components of the $n$-copy Gibbs-rescaled distribution, $w(\noisys | \gamma)_{ijk}$ in decreasing order.
In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
\begin{align}
	&\bmw(\noisys | \gamma)_{\rm{max}} \coloneqq \label{eq:max_slope}\\
	&(3\Z)^{n} \max\limits_{i,j,k}\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \nonumber
\end{align}
where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
Notice that for $0 \leq \epsilon \leq 3/7$, we have $\wn \geq \wp$.
Assume that $n$ is even. 
We then need the sum $\alpha = i+j+k$ to be even, so that the expression remains positive.

Given an even value $\alpha$ for the sum, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	&\bmw(\noisys | \gamma)_{\rm{max}} = \nonumber\\
	&\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} = \nonumber\\
	&\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
\end{align}
The last expression is maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ (greater than $1$).
The threshold value of $1$ is achieved when the noise level $\epsilon$ is equal to
\begin{equation}
	\epsilon_{\rm{th}} \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
\end{equation}
The noise level threshold $\epsilon_{\rm{th}}$ is a decreasing function of $\beta$.
It achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and a value equal to $0$ for
\begin{equation}
	\beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
\end{equation}
For $\beta > \beta_{\rm{th}}$, $\epsilon_{\rm{th}}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
We highlight that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
\begin{equation}
	E_{\rm{max}} - E_0 = \beta_{\rm{th}}^{-1} \ln2.
\end{equation}

The maximum slope finally is
\begin{equation}
\bmw(\noisys | \gamma)_{\rm{max}} =
	\begin{cases}
		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}},\ \hspace{30pt}\rm{(C1)}	\\
		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.\ \hspace{32pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case 1 $\rm{(C1)}$ corresponds to the region labelled by $(i,j,k) = (0,0,0)$.
Case 2 $\rm{(C2)}$ corresponds to the region labelled by 
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
	\end{cases}
\end{equation}
Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
Assuming $E_{\rm{max}} > E_0$, we get the cases:
\begin{itemize}
	\item $\beta = 0$. Then, $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
	This is the unital fragment.
	\item $0 < \beta < \beta_{\rm{th}}$. Then, $0 < \epsilon_{\rm{th}} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\rm{th}}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\rm{th}}$.
	\item $\beta \geq \beta_{\rm{th}}$. Then, $ \epsilon_{\rm{th}} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
\end{itemize}

In $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the corresponding Wigner components are $\bmw(\noisys)_{000}, \bmw(\gamma)_{000}$.
In $\rm{(C2)}$, we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the corresponding Wigner components are $\bmw(\noisys)_{0n0}, \bmw(\gamma)_{0n0}$ ($\bmw(\noisys)_{00n}, \bmw(\gamma)_{00n}$).
The first elbow coordinate expression can finally be expressed as
\begin{equation}\label{eq:first_elb_coords}
	(x_0, L_0) =
	\begin{cases}
		\left( \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n, \wn^n \right), &\rm{(C1)}	\vspace{10pt}\\
		\left( \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n, (3u)^n \right). &\rm{(C2)} 
	\end{cases}
\end{equation}

Consider the distillation process in~\cref{eq:msd_thermal},
\begin{equation*}
		\noisys(\epsilon)\too{n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')\too{\tt} \otimes \gamma_\beta\too{(n-\tt)},
\end{equation*}
with $n > n'$ and $\epsilon > epsilon'$.
A necessary distillation constraint can be defined at the location $x_\star = x_0$ of the initial state's first elbow, expressed as
\begin{equation}\label{eq:first_elbow_constraint}
	\lc{\noisys(\epsilon)\too{n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')\too{\tt}}{\gamma_\beta}(x_\star).
\end{equation}

The Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$, depending on the physical parameters $\epsilon, \epsilon', \beta$.
Specifically, we can get three scenarios:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' < \epsilon  \leq \epsilon_{\rm{th}}$.
	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' \leq \epsilon_{\rm{th}} < \epsilon$.
	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\rm{th}}$.
\end{enumerate}
Note that $\rm{(C1)} \rightarrow \rm{(C2)}$ is impossible because it would imply $\epsilon \leq \epsilon_{\rm{th}} \leq \epsilon' < \epsilon$, a contradiction.

@@

We now compute distillation bounds based on the first elbow constraint in the three possible scenarios.
We express them in terms of the free energy of thermal state $\gamma_\beta$ denoted by
\begin{equation}
	F_\beta \coloneqq \tr[\gamma_\beta H] + \beta^{-1} \tr[\gamma_\beta \ln{\gamma_\beta}] = -\beta^{-1} \ln{\Z_\beta}.
\end{equation}
Substituting coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound}, we get the following necessary conditions:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' < \epsilon  \leq \epsilon_{\rm{th}}$.

@@

	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' \leq \epsilon_{\rm{th}} < \epsilon$.

\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}, \text{ or} \\
	\epsilon &\leq 3 - 6 \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{\tt}{n}} \frac{e^{-\beta E_{\rm{max}}} e^{\frac{\tt}{n}\beta E_0}}{\Z_\beta^{1-\frac{\tt}{n}}}	
\end{align}
This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)} + (E_{\rm{max}} - E_0)(\beta_{\rm{th}} - \beta)}{\beta (E_0 - F_\beta)},
\end{equation}

	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\rm{th}}$.

@@

Consider pure Strange state distillation at high temperatures, $\beta \leq \beta_{\rm{th}}$.
Depending on the noise level of the initial state, we have either a $\rm{(C1)} \rightarrow \rm{(C1)}$ or a $\rm{(C2)} \rightarrow \rm{(C1)}$ scenario.

We compare $R(\beta)$ for different temperatures with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
At every $\beta > 0$, the rates indicate a transition at $\epsilon_{\rm{th}}$.
As $\beta$ increases, the rate becomes stricter.
At the high temperature limit, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
\begin{equation}
	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
\end{equation}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\rm{th}}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
\nick{it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level ($ \leq \epsilon_{\rm{th}}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C2)} \rightarrow \rm{(C1)}$. Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
    }
    \label{fig:distill_bounds_temp}
\end{figure}

>>>>

The more noisy the initial state is, the more copies needed to reach the target. 
We make this idea precise by defining the \emph{noise level threshold} as
\begin{equation}\label{eq:ethresh}
	\begin{split}
	\epsilon_{\star}(n, \tt, \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)\too{n}}{\sigma}}(x) \geq \\
	&{\lc{\rho(\epsilon')\too{\tt}}{\sigma}(x),\ x\in[0,1]\}}.
	\end{split}
\end{equation}
The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\star}(n, \tt, \epsilon', \sigma)$.

\nick{Can also define a distillation bound
\begin{equation}\label{eq:ethresh}
	n_{\star}(\epsilon, \epsilon', \sigma) \coloneqq \min{\{n: \lc{\noisysn}{\sigma} \geq \lc{\noisys(\epsilon')}{\sigma}\}}.
\end{equation}}

@@

In particular, the Wigner distribution of the state can be written as 
\begin{equation}
	\W[\bmx]{\noisys(\epsilon)} = (1-\epsilon)\W[\bmx]{\ketbra{\rm{S}}} + \epsilon\W[\bmx]{\frac{1}{3}\id},
\end{equation}
so we get positive components
\begin{equation}
	u(\epsilon) = \frac{1}{6} -\frac{1}{18}\epsilon
\end{equation}
at the 8 phase space points $\bmx \in \pd[3] \setminus \{\bmo\}$ and a negative component
\begin{equation}
	- v(\epsilon) = - \left( \frac{1}{3} -\frac{4}{9}\epsilon \right)
\end{equation}
at the origin $\bmx = \bmo$.

@@

\ddd{Note the following is relevant: you might have $W_{\bmq} = W_{\bmq'}$ for two different $\bmq$, $\bmq'$. This would make a difference to our calculations for the first elbow. Check this doesn't occur. (If it does, our analysis is still correct, but it simply could be improved).}

@@

We construct component and multiplicity vectors based on the distinct components of the Gibbs-rescaled distribution,
\begin{align}
	\bmm &\coloneqq (1,2,3,3) \\
	\bmw(\noisys) &\coloneqq (-v, u, u, u) \\
	\bmw(\gamma) &\coloneqq \frac{1}{3\Z} \left( e^{-\beta E_0}, e^{-\beta E_0}, e^{-\beta E_1}, e^{-\beta E_2} \right) \\
	\bmw(\noisys | \gamma) &\coloneqq 3\Z \left( -v e^{\beta E_0}, u e^{\beta E_0}, u e^{\beta E_1}, u e^{\beta E_2} \right) \label{eq:bmw_rescaled}
\end{align}

There are four distinct values of the Gibbs-rescaled distribution on the phase space, with the negative Strange component $-v$ corresponding to energy $E_0$ as illustrated in the phase space split in~\cref{fig:pd_split_thermal}.
The Wigner-component vectors $\bmw(\noisys), \bmw(\gamma)$ are then constructed so as to match the four phase space regions.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/pd_split_thermal.pdf}
    \caption{\textbf{Qutrit phase space regions with different Gibbs-rescaled values.}
    The slope is negative in region $1$ and positive in regions $X,Y,Z$.
    It attains a unique value in each region, given by~\cref{eq:bmw_rescaled} respectively.
    }
    \label{fig:pd_split_thermal}
\end{figure}

For notational convenience, we define the index vector
\begin{equation}
	\bmq \coloneqq (n-\alpha,i,j,k),
\end{equation}
where $i,j,k$ are non-negative integers and
\begin{equation*}
	\alpha \coloneqq i+j+k \leq n.
\end{equation*}
The Wigner components of the $n$-copy distributions are now readily provided by~\cref{lem:ncopycomponents}.
Firstly, the $n$-copy multiplicity is given according to~\cref{eq:M} by
\begin{equation}
	m_{ijk} \coloneqq M_{\bmq} = \frac{n!}{i!j!k!(n-\alpha)!} 2^i 3^j 3^k.
\end{equation}
The distribution values that correspond to the same index $\bmq$ are given according to~\cref{eq:W} by
\begin{align}
	w(\noisys)_{ijk} &= (-v)^{n-\alpha} u^{\alpha} \\
	w(\gamma)_{ijk} &= (3\Z)^{-n} e^{-\beta (n-\alpha)E_0} e^{-\beta ( i E_0 + j E_1 + k E_2 )} \\
	w(\noisys | \gamma)_{ijk} &= (3\Z)^{n} (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )}
\end{align}

In order to construct the $n$-copy Lorenz curve of a Strange state in a thermal fragment we need to sort the components of the $n$-copy Gibbs-rescaled distribution, $w(\noisys | \gamma)_{ijk}$ in decreasing order.
In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
\begin{align}
	&\bmw(\noisys | \gamma)_{\rm{max}} \coloneqq \label{eq:max_slope}\\
	&(3\Z)^{n} \max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \nonumber
\end{align}
where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. We assume that $n$ is even, ans so we then need the sum $\alpha = i+j+k$ to be even, so that the expression is positive.

%Given an even value $\alpha$ for the sum, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
%Hence, we have \ddd{Why did the $\Z$ term disappear?}
%\begin{align}
%	\bmw(\noisys | \gamma)_{\rm{max}}
%&=\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ v^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}}  \nonumber\\
%	&= v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
%\end{align}
%If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, and otherwise the maximum occurs at $\alpha = n$.
%The threshold value of $1$ is achieved for this term when the noise level $\epsilon$ is equal to
%\begin{equation}
%	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
%	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
%\end{equation}
%For the case $E_{\rm{max}} = E_0$ this threshold is constant in temperature and given by Since $ E_{\rm max} - E_0 \ge 0$ the threshold $\epsilon_{\star}$ is a decreasing function of $\beta$, and it achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and a value equal to $0$ for
%\begin{equation}
%	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
%\end{equation}
%For $\beta > \beta_{\star}$, $\epsilon_{\star}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
%We highlight that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
%\begin{equation}
%	E_{\rm{max}} - E_0 = kT_{\star} \ln2.
%\end{equation}
%
%The maximum slope \ddd{``maximum slope??''} finally is
%\begin{equation}
%\bmw(\noisys | \gamma)_{\rm{max}} =
%	\begin{cases}
%		v^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\star},\ \hspace{30pt}\rm{(C1)}	\\
%		u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{32pt}\rm{(C2)} 
%	\end{cases}
%\end{equation}
%Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, while case $\rm{(C2)}$ corresponds to the  the conditions 
%\begin{equation}
%	(i,j,k) = 
%	\begin{cases}
%	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
%	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
%	\end{cases}
%\end{equation}
%Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
%Assuming $E_{\rm{max}} > E_0$, we get the cases:
%\begin{itemize}
%	\item $\beta = 0$. Then, $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
%	This is the unital fragment.
%	\item $0 < \beta < \beta_{\star}$. Then, $0 < \epsilon_{\star} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\star}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\star}$.
%	\item $\beta \geq \beta_{\star}$. Then, $ \epsilon_{\star} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
%\end{itemize}

In $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the corresponding Wigner components are $\bmw(\noisys)_{000}, \bmw(\gamma)_{000}$.
In $\rm{(C2)}$, we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the corresponding Wigner components are $\bmw(\noisys)_{0n0}, \bmw(\gamma)_{0n0}$ ($\bmw(\noisys)_{00n}, \bmw(\gamma)_{00n}$).
The first elbow coordinate expression can finally be expressed as
\begin{equation}\label{eq:first_elb_coords}
	(x_0, L_0) =
	\begin{cases}
		\left( \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n, v^n \right), &\rm{(C1)}	\vspace{10pt}\\
		\left( \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n, (3u)^n \right). &\rm{(C2)} 
	\end{cases}
\end{equation}

Consider the distillation process in~\cref{eq:msd_thermal},
\begin{equation*}
		\noisys(\epsilon)\too{n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')\too{\tt} \otimes \gamma_\beta\too{(n-\tt)},
\end{equation*}
with $n > n'$ and $\epsilon > \epsilon'$.
A necessary distillation constraint can be defined at the location $x_\star = x_0$ of the initial state's first elbow, expressed as
\begin{equation}\label{eq:first_elbow_constraint}
	\lc{\noisys(\epsilon)\too{n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')\too{\tt}}{\gamma_\beta}(x_\star).
\end{equation}

The Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$, depending on the physical parameters $\epsilon, \epsilon', \beta$.
Specifically, we can get three scenarios:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\star}$.
\end{enumerate}
Note that $\rm{(C1)} \rightarrow \rm{(C2)}$ is impossible because it would imply $\epsilon \leq \epsilon_{\star} \leq \epsilon' < \epsilon$, a contradiction.

@@

We now compute distillation bounds based on the first elbow constraint in the three possible scenarios.
We express them in terms of the free energy of thermal state $\gamma_\beta$ denoted by
\begin{equation}
	F_\beta \coloneqq \tr[\gamma_\beta H] + \beta^{-1} \tr[\gamma_\beta \ln{\gamma_\beta}] = -\beta^{-1} \ln{\Z_\beta}.
\end{equation}
Substituting coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound}, we get the following necessary conditions:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.

@@

	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.

\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}, \text{ or} \\
	\epsilon &\leq 3 - 6 \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{\tt}{n}} \frac{e^{-\beta E_{\rm{max}}} e^{\frac{\tt}{n}\beta E_0}}{\Z_\beta^{1-\frac{\tt}{n}}}	
\end{align}
This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)} + (E_{\rm{max}} - E_0)(\beta_{\star} - \beta)}{\beta (E_0 - F_\beta)},
\end{equation}

	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\star}$.

@@

Consider pure Strange state distillation at high temperatures, $\beta \leq \beta_{\star}$.
Depending on the noise level of the initial state, we have either a $\rm{(C1)} \rightarrow \rm{(C1)}$ or a $\rm{(C2)} \rightarrow \rm{(C1)}$ scenario.

We compare $R(\beta)$ for different temperatures with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
At every $\beta > 0$, the rates indicate a transition at $\epsilon_{\star}$.
As $\beta$ increases, the rate becomes stricter.
At the high temperature limit, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
\begin{equation}
	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
\end{equation}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\star}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\star}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
\nick{it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level ($ \leq \epsilon_{\star}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C2)} \rightarrow \rm{(C1)}$. Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
    }
    \label{fig:distill_bounds_temp}
\end{figure}
